\bf Primal-dual algorithm for computing Nash equilibria in sequential games with imcomplete information

### 2015-02-19 nips2015.tex
wip

\usepackage[section]{placeins}

@@

\begin{abstract}
We present a simple primal-dual algorithm with a low cost per iteration for computing Nash $\epsilon$-equilibria in two-person zero-sum sequential games with imcomplete information and perfect recall (like Texas Hold'em Poker), which converges after $\mathcal{O}(1/\epsilon)$ basic iterations
(i.e iterations involving no
%o only involving basic operations like matvec, clipping, etc., and no
calls to external first-order oracles, etc.). %% Our algorithm is applicable to a broad class of two-person zero-sum games including simultaneous games and sequential games with imcomplete information and perfect recall. The applicability to the latter kind of games is thanks to the sequen e-form representation von Stengel's \cite{von1996efficient}
Our algorithm derives from the general primal-dual algorithm developed
% by Chambolle and Pock
in \cite{chambolle2010, chambolle2014ergodic}. It should be noted that the latter primal-dual algorithm is not directly applicable to compute Nash equilibria for the aforementioned games considered here since the strategy profiles of players are polyhedra, so complex that it is not possible
% (for example, simplexes for simultaneous games, and intersections of hyperplanes and nonnegative orthants, for sequential games)
 to effectively compute % (i.e using non-iterative procedures, etc.)
euclidean
% (metric)%
 projections (the proximal operators) thereupon.
The core of our technique is to dualize the linear constraints that form the player's strategy profile, thus obtainining an equivalent saddle-point problem which is amenable to the primal-dual scheme. Unlike the EGT (Excessive Gap Technique) recently used in \cite{hoda2010smoothing, gilpinfirst}, our algorithm has a cheap and constant cost per iteration. As an application, we apply our algorithm to solve Kuhn 3-card Poker \cite{kuhn}.
%% We conclude by extending our results to tackle Nash equilibrium problems with even more general strategy profiles, where the nonnegativity constraints on realization plans are replaced with more general convex sets.
\end{abstract}

@@

\subsection{Some notation}
Given positive integers $m$ and $n$, $\mathbb{R}^{m \times n}$ denotes
the space of all $m$-by-$n$ real matrices, and $0_{m,n}$ denotes the $m$-by-$n$ matrix of zeros.
$\mathbb{R}^{n}_+ := \{z \in \mathbb{R}^{n}\text{ }|\text{ } z \geq 0\}$ is the nonnegative $n$-dimensional \textit{orthant}.  The components of a vector $z \in \mathbb{R}^,$ will be denoted $z_0$, $z_1$, ..., $z_{n-1}$. The notation ``$z \ge 0$'' means that all the components of $z$ are nonnegative. For a vector $z = (z_0, z_1, ..., z_{n-1}) \in \mathbb{R}^n$, %% $\|z\|$ denotes the $2$-\textit{norm} of $z$ defined by $\|z\| := \sqrt{z^Tz} = \sqrt{\sum_{j=0}^{n - 1}{z_j^2}}$.
$(z)_+:=\text{max}(0, z) \in \mathbb{R}^{n}_+$ is the point-wise maximum of $z$ with 0. For example, $((-2, \pi))_+ = (max(-2, 0), max(\pi, 0)) = (0, \pi)$.  The operator $(.)_+$ is the well-known (multi-dimensional) \textit{ramp} function.

The \textit{spectral norm} of a matrix $K$, denoted $\|K\|$, is defined to be the largest \textit{singular value} of $K$, i.e the largest \textit{eigen-value} of $K^TK$ (or equivalently, of $KK^T$).

@@

and the dual LCP problem
\begin{equation}
  \begin{aligned}
    & \underset{x,q}{\text{maximize}}
    && -q_0 \\
    & \text{subject to}
    && -A^Tx - E_2^Tq \leq 0,\\
    &&&\hspace{4.5em} E_1x = e_1,\\
    &&&\hspace{5.5em} x \ge 0.
  \end{aligned}
  \label{eq:dual_pb}
\end{equation}
The vectors $p = (p_0, p_1, ..., p_{l_2 - 1}) \in \mathbb{R}^{l_2}$ and $q = (q_0, q_1, ..., q_{l_1 - 1}) \in \mathbb{R}^{l_1}$ are dual variables. 
$A$ is the \textit{payoff matrix} and each $E_k$ is a matrix whose entries are $-1$, $0$ or $1$, and $e_k$ is a vector of the form $[1, 0, ..., 0]$. In this so-called \textit{sequence-form} representation, the strategy profile of player $k$ is the polyhedron
\begin{equation}
  Q_k := \{z \in \mathbb{R}^n_+ |\text{ }E_kz = e_k\}
\label{eq:polyhedron}
\end{equation}
Note that $p^Te_1 = p_0$ and $q^Te_2 = q_0$ by definition of $e_1$ and $e_2$. At a feasible point $(x, y, p, q)$, the \textit{duality gap} $\mathcal{G}(x, y, p, q)$ of primal-dual pair of problems is given by\footnote{The last inequality being due to \textit{weak duality}.}
\begin{equation}
  0 \le \mathcal{G}(x, y, p, q) := p_0 - (-q_0) = p_0 + q_0
  \label{eq:dgap}
\end{equation}
Define the following closed convex sets
\begin{equation}
  \begin{aligned}
  \Sigma_1 &:= \{(y, p) \in \mathbb{R}^{n_2} \times \mathbb{R}^{l_1}\text{ }|\text{ } -Ay + E_1^Tp \ge 0, E_2y = e_2, y \ge 0\}\\
  \Sigma_2 &:= \{(x, q) \in \mathbb{R}^{n_1} \times \mathbb{R}^{l_2}\text{ }|\text{ } -A^Tx - E_2^Tq \le 0, E_1x = e_1, x \ge 0\}
  \end{aligned}
  \label{eq:feasibility}
\end{equation}
It was shown (see Theorem 3.14 of \cite{vonequilibrium}) that a pair $(x, y)$ is a solution to the LCP problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb} if (and only if) there exist vectors $p$ and $q$ such that $(y, p) \in \Sigma_1$ and $(x, q) \in \Sigma_2$. Thus the problem of finding a Nash equilibrium is equivalent to the problem of finding a point in the cartesian product $\Sigma_1 \times \Sigma_2$. Moreover, at equilibria, \textit{strong duality} holds and the value of the game equals $p_0 = -q_0$, i.e the duality gap $\mathcal{G}(x, y, p, q)$ defined in \eqref{eq:dgap} vanishes at equilibria.

@@

\begin{remark}  
It should be noted that even though problem \eqref{eq:primal_pb} is in theory, amenable to classical tools like LCP (\textit{Linear Constraint Programming}), the class of games considered here (sequential games with imcomplete information) are exceedingly larger than what such programs can handle (see \cite{hoda2010smoothing}).
\end{remark}

Solving problem \eqref{eq:primal_pb} exactly is impossible in practice \textbf{Cite Koller!!!}, and such a precision doesn't have any fundamental advantage. Instead, it is customary compute so-called Nash $\epsilon$-equlibria.

\begin{definition}(\textbf{Nash $\epsilon$-equilibria})
Given a small margin $\epsilon > 0$, a Nash $\epsilon$-equilibrium is a pair $(x^*, y^*)$ of realization plans such that there exists dual vectors $p^*$ and $q^*$ for problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb} such that the duality gap at $(x^*, y^*, p^*, q^*)$ doesn't exceed $\epsilon$. That is,
\begin{equation}
  0 \le \mathcal{G}(x^*, y^*, p^*, q^*) \le \epsilon
\label{eq:approx_pb}
\end{equation}
\end{definition}

@@

\section{Useful convex-analysis}
\label{sec:notation}
We will need the following notations and concepts from convex-analysis in the sequel.
Given a \textit{convex subset} $C$ of $\mathbb{R}^n$, $i_C$ denotes its \textit{indicator function} defined by
\begin{equation}
  i_C(x) = \begin{cases}
    0, &\mbox{if } x \in C\\
    +\infty, &\mbox{otherwise}.
    \end{cases}
  \end{equation}
Note that $i_{C \cap D} = i_C + i_D$. The \textit{euclidean projection} onto $C$, denoted $\Pi_C$, is the function
$\Pi: \mathbb{R}^n \mapsto C$ which maps a point $x \in \mathbb{R}^n$ to the (necessarily unique) point $\Pi_C(x)$ of $C$ which is closest to $x$. Precisely,
\begin{equation}
  \Pi_C(x) := \underset{c \in C}{argimin}\text{ }\|c - x\|^2
\end{equation}
For example, the euclidean projections onto the nonnegative orthant and the closed unit-disk $\bar{\Delta}$
% := \{x|\|x\| \le 1\}$
are $\Pi_{\mathbb{R}^n_+}(x) \equiv (x)_+$ and $\Pi_{\bar{\Delta}}(z) \equiv \dfrac{z}{max(\|z\|, 1)}$ respectively.

Let $f : \mathbb{R}^n \rightarrow [-\infty, +\infty]$ be a \textit{proper convex lower semi-continous function}
(\textit{p.c.l.s.c} for short). The \textit{convex conjugate} of $f$ is the function $f^*: \mathbb{R}^n \rightarrow [-\infty, +\infty]$ is defined by
\begin{equation}
  x \mapsto f^*(x) := \underset{z \in \mathbb{R}^n}{\text{max}}\text{ }z^Tx - f(z)
\end{equation}

For example $i_{\mathbb{R}^{n}_+}^*(x) \equiv i_{\mathbb{R}^{n}_+}(-x)$; $(a^Tx)^* \equiv i_{\{0\}}(x - a)$; and $(\frac{1}{2}\|x\|^2)^* \equiv \frac{1}{2}\|x\|^2$. One easily verifies that $f^{**} = f$. Given $\tau > 0$, the \textit{proximal operator} of $f$ of rank
$\tau$, denoted $\text{prox}_{\tau f}$, is the function which maps a point $x \in \mathbb{R}^n$ to the (necessarily
unique) solution of the problem
\begin{equation}
  \underset{z \in \mathbb{R}^n}{argmin}\text{ }\frac{1}{2}\|z - x\|^2 + \tau f(z)
\end{equation}

It is easy to see that if $f$ is the indicator function of a convex set $C$, then $\text{prox}_{\tau f} = \Pi_C, \forall \tau > 0$. In this sense, proximal operators can be seen
as a generalization of euclidean projections.

@@

%% Theorem \ref{thm:pd}, can be interpreted as follows: 2 players $x$ (player 1)  and $y$ (player 2) go heads-on in a zero-sum game with payoff matrix $A$. Their strategy, profiles are $Q_1$ and $Q_2$ respectively, meaning that if player $j$ players a strategy which is outside $Q_k$ then they are panalized by inflicting an infinite loss yupon them. To remedy this, they recruit assistants $u$ and $v$, whose sole goal is to preven the ...
\begin{proof}
Recall the definition of the feasibility sets $\Sigma_i$ from equation \eqref{eq:feasibility}.
The optimal value in the dual LCP problem \eqref{eq:primal_pb} can be computed as 
\begin{eqnarray*}
  \begin{aligned}
    p_0^* &= \text{min}\{p_0\text{ }|\text{ } (y, p) \in \Sigma_1, p = (p_0, p_1, ..., q_{l_1-1})\}\\
    &= \underset{y,p}{\text{min}}\text{ }i_{\mathbb{R}^{n_2}_+}(y) + p_0 + i_{\mathbb{R}^{n_1}_+}(-Ay + E_1^Tp) + i_{\{0\}}(E_2y - e_2)\\
    &= \underset{y,p}{\text{min}}\text{ }G_1(y,p) + i_{\mathbb{R}^{n_1}_+}(-Ay + E_1^Tp) + i_{\{0\}}(E_2y - e2)\\
    &= \underset{y,p}{\text{min}}\text{ }G_1(y,p) + \underset{x \geq 0}{\text{max}}\text{ }x^T(Ay - E_1^Tp) + \underset{q}{\text{max}}\text{ }q^T(E_2y - e_2)\\
    &= \underset{y,p}{\text{min}}\text{ }G_1(y,p) + \underset{x, q}{\text{max}}\text{ }x^TAy - x^TE_1^Tp + q^TE_2y - i_{\mathbb{R}^{n_1}_+}(x) - q^Te_2\\
    &= \underset{y,p}{\text{min}}\text{ }G_1(y,p) + \underset{x, q}{\text{max}}\text{ }x^TAy - x^TE_1^Tp + q^TE_2y - (i_{\mathbb{R}^{n_1}_+}(x) + q_0)\\
    &= \underset{y,p}{\text{min}}\text{ }G_1(y,p) + \underset{x,q}{\text{max}}\text{ }\begin{bmatrix}x\\q\end{bmatrix}^TK\begin{bmatrix}y\\p\end{bmatrix} - G_2(x, q) \\
      &= \underset{y,p}{\text{min}}\text{ }G_1(y,p) + G_2^*\left(K\begin{bmatrix}y\\p\end{bmatrix}\right)
  \end{aligned}
  \label{eq:a}
\end{eqnarray*}
Thus the LCP problem \eqref{eq:primal_pb} can be written as 
\begin{equation}
  \underset{y,p}{\text{minimize}}\text{ }G_1(y,p) + G_2^*\left(K\begin{bmatrix}y\\p\end{bmatrix}\right)
\end{equation}
Similarly, the optimal value in the dual LCP problem \eqref{eq:dual_pb} writes
\begin{eqnarray*}
  \begin{aligned}
 -q_0^* &= \text{max}\{-q_0\text{ }|\text{ } (x, q) \in \Sigma_2, q = (q_0, q_1, ..., q_{l_2-1})\}\\
    &= \underset{x,q}{\text{max}}\text{ }-(i_{\mathbb{R}^{n_1}_+}(x) + q_0) - i_{\mathbb{R}^{n_2}_+}(A^Tx+E_2^Tq) - i_{\{0\}}(E_1x - e_1)\\
    &= \underset{x,q}{\text{max}}\text{ }-G_2(x, q) - \underset{y \geq 0}{\text{max}}\text{ }y^T(-A^Tx + E_2^Tq) - \underset{p}{\text{max}}\text{ }p^T(E_1x-e_1)\\
    &= \underset{x,q}{\text{max}}\text{ }-G_2(x, q) -\underset{y,p}{\text{max}}\text{ }-(y^TA^Tx -p^TE_1x + y^TE_2^Tp)-(i_{\mathbb{R}^{n_2}_+}(y) + p^Te_1)\\
    &= \underset{x,q}{\text{max}}\text{ }-G_2(x, q)-\underset{y,p}{\text{max}}\text{ }-
 \begin{bmatrix}y\\p\end{bmatrix}K^T\begin{bmatrix}x\\q\end{bmatrix}-G_1(y,p)\\
   &= \underset{x,q}{\text{max}}\text{ }-G_2(x, q)-G_1^*\left(-K^T\begin{bmatrix}x\\q\end{bmatrix}\right)
  \end{aligned}
\end{eqnarray*}
Thus the LCP problem \eqref{eq:dual_pb} is equivalent to
\begin{equation}
  \underset{x,q}{\text{maximize}}\text{ }-G_1^*\left(-K^T\begin{bmatrix}x\\q\end{bmatrix}\right) - G_2(x, q)
\end{equation}

But these last two equations are simply the primal and dual formulations respectively, of the saddle-point problem \eqref{eq:unconstrained_pb}, and we are done.

@@

\subsection{The proposed algorithm and its $\mathcal{O}(1/\epsilon)$ convergence}
According to Theorem \ref{thm:pd}, solving the Nash equilibrium LCP problems \eqref{eq:primal_pb}, \eqref{eq:dual_pb} is equivalent to solving the saddle-point problem \eqref{eq:unconstrained_pb}.
In order to apply Algorithm 39 of \cite{chambolle2010}, we need the proximal operators of
$G_1$ and $G_2$. Now, both functions are \textit{p.c.l.s.c} and their proximal operators are given by
  \begin{equation}
    \left .
    \begin{split}
      \text{prox}_{\tau G_1} : \mathbb{R}^{n_2} \times \mathbb{R}^{l_1} &\rightarrow \mathbb{R}^{n_2} \times \mathbb{R}^{l_1}\\
      (y, p) &\mapsto ((y)_+, p - \tau e_1)\\
    \end{split}
    \right\}
  \end{equation}

>>>>

%% prevent figures, algorithms, etc., floating across subsections
\usepackage[section]{placeins}
\makeatletter
\AtBeginDocument{%
  \expandafter\renewcommand\expandafter\subsection\expandafter{%
    \expandafter\@fb@secFB\subsection
  }%
}
\makeatother

@@

\begin{abstract}
We present a simple primal-dual algorithm with a low cost per iteration for computing Nash $\epsilon$-equilibria in two-person zero-sum sequential games with imcomplete information and perfect recall (like Texas Hold'em Poker), which converges after $\mathcal{O}(1/\epsilon)$ basic iterations
(i.e iterations involving no
%o only involving basic operations like matvec, clipping, etc., and no
calls to external first-order oracles, etc.). %% Our algorithm is applicable to a broad class of two-person zero-sum games including simultaneous games and sequential games with imcomplete information and perfect recall. The applicability to the latter kind of games is thanks to the sequen e-form representation von Stengel's \cite{von1996efficient}
Our algorithm derives from the general primal-dual algorithm developed
% by Chambolle and Pock
in \cite{chambolle2010, chambolle2014ergodic}. It should be noted that the latter primal-dual algorithm is not directly applicable to compute Nash equilibria for the aforementioned games considered here since the strategy profiles of players (polyhedra) are so complex that it is not possible
% (for example, simplexes for simultaneous games, and intersections of hyperplanes and nonnegative orthants, for sequential games)
 to effectively compute % (i.e using non-iterative procedures, etc.)
euclidean
% (metric)%
 projections (the proximal operators) thereupon.
The core of our technique is to dualize the linear constraints that form the player's strategy profile, thus obtainining an equivalent saddle-point problem which is amenable to the primal-dual scheme. Unlike the EGT (Excessive Gap Technique) recently used in \cite{hoda2010smoothing, gilpinfirst}, our algorithm has a cheap and constant cost per iteration. As an application, we apply our algorithm to solve Kuhn 3-card Poker.
%% We conclude by extending our results to tackle Nash equilibrium problems with even more general strategy profiles, where the nonnegativity constraints on realization plans are replaced with more general convex sets.
\end{abstract}

@@

\subsection{Some notation}
Let $m$ and $n$ be positive integers.
$\mathbb{R}^{n}_+ := \{z \in \mathbb{R}^{n}\text{ }|\text{ } z \geq 0\}$ is the nonnegative $n$-dimensional \textit{orthant}.  The components of a vector $z \in \mathbb{R}^n$ will be denoted $z_0$, $z_1$, ..., $z_{n-1}$ (indexing begins from $0$, and not $1$). The notation ``$z \ge 0$'' means that all the components of $z$ are nonnegative. For a vector $z = (z_0, z_1, ..., z_{n-1}) \in \mathbb{R}^n$, %% $\|z\|$ denotes the $2$-\textit{norm} of $z$ defined by $\|z\| := \sqrt{z^Tz} = \sqrt{\sum_{j=0}^{n - 1}{z_j^2}}$.
$(z)_+:=\text{max}(0, z) \in \mathbb{R}^{n}_+$ is the point-wise maximum of $z$ with $0$. For example, $((-2, \pi))_+ = (max(-2, 0), max(\pi, 0)) = (0, \pi)$.  The operator $(.)_+$ is the well-known (multi-dimensional) \textit{ramp} function.

$\mathbb{R}^{m \times n}$ denotes the space of all $m$-by-$n$ real matrices, and $0_{m,n}$ denotes the $m$-by-$n$ matrix of zeros. Given a matrix $A \in \mathbb{R}^{m \times n}$, its entries will be donoted $A_{i,j}$ so that
\[
A :=\left[
\begin{array}{cccc}
A_{0,0} & A_{0,1} & \cdots & A_{0,n-1} \\
A_{1,0} & A_{1,1} & \cdots & A_{1,n-1} \\
\vdots & \vdots & \ddots & \vdots\\
A_{m-1,0} & A_{m-1,1} & \cdots & A_{m-1,n-1}
\end{array}\right]
\]
The \textit{spectral norm} of a matrix $A$, denoted $\|A\|$, is defined to be the largest \textit{singular value} of $A$, i.e the largest \textit{eigen-value} of $A^TA$ (or equivalently, of $AA^T$).

@@

and the dual LCP problem
\begin{equation}
  \begin{aligned}
    & \underset{x,q}{\text{maximize}}
    && -q_0 \\
    & \text{subject to}
    && -A^Tx - E_2^Tq \leq 0,\\
    &&&\hspace{4.5em} E_1x = e_1,\\
    &&&\hspace{5.5em} x \ge 0.
  \end{aligned}
  \label{eq:dual_pb}
\end{equation}
The vectors $p = (p_0, p_1, ..., p_{l_2 - 1}) \in \mathbb{R}^{l_2}$ and $q = (q_0, q_1, ..., q_{l_1 - 1}) \in \mathbb{R}^{l_1}$ are dual variables. 
$A$ is the \textit{payoff matrix} and each $E_k$ is a matrix whose entries are $-1$, $0$ or $1$, and each $e_k$ is a vector of the form $[1, 0, ..., 0]$. In this so-called \textit{sequence-form} representation, the strategy profile of player $k$ is the polyhedron
\begin{equation}
  Q_k := \{z \in \mathbb{R}^n_+ |\text{ }E_kz = e_k\}
\label{eq:polyhedron}
\end{equation}
Note that $p^Te_1 = p_0$ and $q^Te_2 = q_0$ by definition of $e_1$ and $e_2$. At a feasible point $(y, p, x, q)$, the \textit{duality gap} $\mathcal{G}(y, p, x, q)$ of these primal-dual pair of LCP problems is given by\footnote{The inequality being due to \textit{weak duality}.}
\begin{equation}
  0 \le \mathcal{G}(y, p, x, q) := p_0 - (-q_0) = p_0 + q_0
  \label{eq:dgap}
\end{equation}
Define the following closed convex sets
\begin{equation}
  \begin{aligned}
  \Sigma_1 &:= \{(y, p) \in \mathbb{R}^{n_2} \times \mathbb{R}^{l_1}\text{ }|\text{ } -Ay + E_1^Tp \ge 0, E_2y = e_2, y \ge 0\}\\
  \Sigma_2 &:= \{(x, q) \in \mathbb{R}^{n_1} \times \mathbb{R}^{l_2}\text{ }|\text{ } -A^Tx - E_2^Tq \le 0, E_1x = e_1, x \ge 0\}
  \end{aligned}
  \label{eq:feasibility}
\end{equation}
It was shown (see Theorem 3.14 of \cite{vonequilibrium}) that a pair $(x, y)$ is a solution to the LCP problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb} if (and only if) there exist vectors $p$ and $q$ such that $(y, p) \in \Sigma_1$ and $(x, q) \in \Sigma_2$. Thus the problem of finding a Nash equilibrium is equivalent to the problem of finding a point in the cartesian product $\Sigma_1 \times \Sigma_2$. Moreover, at equilibria, \textit{strong duality} holds and the value of the game equals $p_0 = -q_0$, i.e the duality gap $\mathcal{G}(y, p, x, q)$ defined in \eqref{eq:dgap} vanishes at equilibria.

@@

\begin{remark}  
It should be noted that for the the class of games considered here (sequential games with imcomplete information), the LCP problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb} are exceedingly larger than what state-of-the-art LCP solvers can handle. See \cite{hoda2010smoothing}.
\end{remark}

Solving the LCP problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb} exactly is impossible in practice \textbf{Cite Koller!!!}, and such a precision doesn't have any fundamental advantage. Instead, it is customary compute so-called Nash $\epsilon$-equlibria.

\begin{definition}(\textbf{Nash $\epsilon$-equilibria})
Given a small margin $\epsilon > 0$, a Nash $\epsilon$-equilibrium is a pair $(x^*, y^*)$ of realization plans such that there exists dual vectors $p^*$ and $q^*$ for problems \eqref{eq:primal_pb} and \eqref{eq:dual_pb} such that the duality gap at $(y^*, p^*, x^*, q^*)$ doesn't exceed $\epsilon$. That is,
\begin{equation}
  0 \le \mathcal{G}(y^*, p^*, x^*, q^*) \le \epsilon
\label{eq:approx_pb}
\end{equation}
\end{definition}

@@

\section{Useful convex-analysis}
\label{sec:notation}
We will need the following notations and concepts from convex-analysis in the sequel.
Given a \textit{convex subset} $C$ of $\mathbb{R}^n$, $i_C$ denotes its \textit{indicator function} defined by
\begin{equation}
  i_C(x) = \begin{cases}
    0, &\mbox{if } x \in C\\
    +\infty, &\mbox{otherwise}.
    \end{cases}
  \end{equation}
Note that $i_{C \cap D} = i_C + i_D$. The \textit{euclidean projection} onto $C$, denoted $\Pi_C$, is the function
$\Pi: \mathbb{R}^n \mapsto C$ which maps a point $x \in \mathbb{R}^n$ to the (necessarily unique) point $\Pi_C(x)$ of $C$ which is closest to $x$. Precisely,
\begin{equation}
  \Pi_C(x) := \underset{c \in C}{argimin}\text{ }\|c - x\|^2
\end{equation}
As an example, the euclidean projections onto the nonnegative orthant and the closed unit-disk $\bar{\Delta}$
% := \{x|\|x\| \le 1\}$
are $\Pi_{\mathbb{R}^n_+}(x) \equiv (x)_+$ and $\Pi_{\bar{\Delta}}(z) \equiv \dfrac{z}{max(\|z\|, 1)}$ respectively.

Let $f : \mathbb{R}^n \rightarrow (-\infty, +\infty]$ be a \textit{proper} (meaning that it is not identically $\infty$) convex function.
%% \textit{proper convex lower semi-continous function}
%% (\textit{p.c.l.s.c} for short).
The \textit{convex conjugate} of $f$ is the function $f^*: \mathbb{R}^n \rightarrow (-\infty, +\infty]$ defined by
\begin{equation}
  x \mapsto f^*(x) := \underset{z \in \mathbb{R}^n}{\text{max}}\text{ }z^Tx - f(z)
\end{equation}
For example, $i_{\mathbb{R}^{n}_+}^*(x) \equiv i_{\mathbb{R}^{n}_+}(-x)$; $(a^Tx)^* \equiv i_{\{0\}}(x - a)$; and $(\frac{1}{2}\|x\|^2)^* \equiv \frac{1}{2}\|x\|^2$. One easily verifies that $f^{**} = f$, if $f$ is \textit{lower semi-continuous}. The \textit{domain} of $f$ is defined by
\begin{equation}
dom f := \{x \in \mathbb{R}^n | f(x) < \infty\}
\end{equation}
If $dom f = \mathbb{R}^{n}$, then we say $f$ has \textit{full domain}.
Note that if $x \mapsto \dfrac{f(x)}{\|x\|}$ is unbounded, then $f^*$ has full domain.

Let $f$ be as above. Given $\tau > 0$, the \textit{proximal operator} of $f$, at rank
$\tau$, denoted $\text{prox}_{\tau f}$, is the function which maps a point $x \in \mathbb{R}^n$ to the (necessarily
unique) solution of the problem
\begin{equation}
  \underset{z \in \mathbb{R}^n}{argmin}\text{ }\frac{1}{2}\|z - x\|^2 + \tau f(z)
\end{equation}
It is easy to see that if $f$ is the indicator function of a convex set $C$, then $\text{prox}_{\tau f} = \Pi_C, \forall \tau > 0$. In this sense, proximal operators can be seen
as a generalization of euclidean projections.

@@

%% Theorem \ref{thm:pd}, can be interpreted as follows: 2 players $x$ (player 1)  and $y$ (player 2) go heads-on in a zero-sum game with payoff matrix $A$. Their strategy, profiles are $Q_1$ and $Q_2$ respectively, meaning that if player $j$ players a strategy which is outside $Q_k$ then they are panalized by inflicting an infinite loss yupon them. To remedy this, they recruit assistants $u$ and $v$, whose sole goal is to preven the ...
\begin{proof}
Recall the definition of the feasibility sets $\Sigma_i$ from equation \eqref{eq:feasibility}.
The optimal value in the dual LCP problem \eqref{eq:primal_pb} can be computed as 
\begin{eqnarray*}
  \begin{aligned}
    p_0^* &= \text{min}\{p_0\text{ }|\text{ } (y, p) \in \Sigma_1, p = (p_0, p_1, ..., q_{l_1-1})\}\\
    &= \underset{y,p}{\text{min}}\text{ }i_{\mathbb{R}^{n_2}_+}(y) + p_0 + i_{\mathbb{R}^{n_1}_+}(-Ay + E_1^Tp) + i_{\{0\}}(E_2y - e_2)\\
    &= \underset{y,p}{\text{min}}\text{ }G_1(y,p) + i_{\mathbb{R}^{n_1}_+}(-Ay + E_1^Tp) + i_{\{0\}}(E_2y - e2)\\
    &= \underset{y,p}{\text{min}}\text{ }G_1(y,p) + \underset{x \geq 0}{\text{max}}\text{ }x^T(Ay - E_1^Tp) + \underset{q}{\text{max}}\text{ }q^T(E_2y - e_2)\\
    &= \underset{y,p}{\text{min}}\text{ }G_1(y,p) + \underset{x, q}{\text{max}}\text{ }x^TAy - x^TE_1^Tp + q^TE_2y - i_{\mathbb{R}^{n_1}_+}(x) - q^Te_2\\
    &= \underset{y,p}{\text{min}}\text{ }G_1(y,p) + \underset{x, q}{\text{max}}\text{ }x^TAy - x^TE_1^Tp + q^TE_2y - (i_{\mathbb{R}^{n_1}_+}(x) + q_0)\\
    &= \underset{y,p}{\text{min}}\text{ }G_1(y,p) + \underset{x,q}{\text{max}}\text{ }\begin{bmatrix}x\\q\end{bmatrix}^TK\begin{bmatrix}y\\p\end{bmatrix} - G_2(x, q) \\
      &= \underset{y,p}{\text{min}}\text{ }G_1(y,p) + G_2^*\left(K\begin{bmatrix}y\\p\end{bmatrix}\right)
  \end{aligned}
  \label{eq:a}
\end{eqnarray*}
Thus the LCP problem \eqref{eq:primal_pb} can be written as 
\begin{equation}
  \underset{y,p}{\text{minimize}}\text{ }G_1(y,p) + G_2^*\left(K\begin{bmatrix}y\\p\end{bmatrix}\right)
\end{equation}
Similarly, the optimal value in the dual LCP problem \eqref{eq:dual_pb} writes
\begin{eqnarray*}
  \begin{aligned}
 -q_0^* &= \text{max}\{-q_0\text{ }|\text{ } (x, q) \in \Sigma_2, q = (q_0, q_1, ..., q_{l_2-1})\}\\
    &= \underset{x,q}{\text{max}}\text{ }-(i_{\mathbb{R}^{n_1}_+}(x) + q_0) - i_{\mathbb{R}^{n_2}_+}(A^Tx+E_2^Tq) - i_{\{0\}}(E_1x - e_1)\\
    &= \underset{x,q}{\text{max}}\text{ }-G_2(x, q) - \underset{y \geq 0}{\text{max}}\text{ }y^T(-A^Tx + E_2^Tq) - \underset{p}{\text{max}}\text{ }p^T(E_1x-e_1)\\
    &= \underset{x,q}{\text{max}}\text{ }-G_2(x, q) -\underset{y,p}{\text{max}}\text{ }-(y^TA^Tx -p^TE_1x + y^TE_2^Tp)-(i_{\mathbb{R}^{n_2}_+}(y) + p^Te_1)\\
    &= \underset{x,q}{\text{max}}\text{ }-G_2(x, q)-\underset{y,p}{\text{max}}\text{ }-
 \begin{bmatrix}y\\p\end{bmatrix}K^T\begin{bmatrix}x\\q\end{bmatrix}-G_1(y,p)\\
   &= \underset{x,q}{\text{max}}\text{ }-G_2(x, q)-G_1^*\left(-K^T\begin{bmatrix}x\\q\end{bmatrix}\right)
  \end{aligned}
\end{eqnarray*}
Thus the LCP problem \eqref{eq:dual_pb} is equivalent to
\begin{equation}
  \underset{x,q}{\text{maximize}}\text{ }-G_1^*\left(-K^T\begin{bmatrix}x\\q\end{bmatrix}\right) - G_2(x, q)
\end{equation}
But these last two equations are simply the primal and dual formulations respectively, of the saddle-point problem \eqref{eq:unconstrained_pb}, and we are done.

@@

\subsection{The proposed algorithm and its $\mathcal{O}(1/\epsilon)$ convergence}
According to Theorem \ref{thm:pd}, solving the Nash equilibrium LCP problems \eqref{eq:primal_pb}, \eqref{eq:dual_pb} is equivalent to solving the saddle-point problem \eqref{eq:unconstrained_pb}.
In order to apply Algorithm 39 of \cite{chambolle2010}, we need formulae for the proximal operators of
$G_1$ and $G_2$. Now, either of $G_1$ and $G_2$ is a separable sum of the indicator function of a convex set, whose prox is simply the euclidean projection onto the set,  and a linear transformation $z \mapsto a^Tz$ whose prox is simply $z \mapsto z - \tau a$. Thus,  one computes their respective proximal operators $\text{prox}_{\tau G_1} : \mathbb{R}^{n_2} \times \mathbb{R}^{l_1} \rightarrow \mathbb{R}^{n_2} \times \mathbb{R}^{l_1}$, $\text{prox}_{\sigma G_2}: \mathbb{R}^{n_1} \times \mathbb{R}^{l_2} \rightarrow \mathbb{R}^{n_1} \times \mathbb{R}^{l_2}$ as
  \begin{equation}
    \text{prox}_{\tau G_1}(y, p) = ((y)_+, p - \tau e_1), \hspace{1em} \text{prox}_{\sigma G_2}(x, q) = ((x)_+, q - \sigma e_2)
  \end{equation}

Finally, applying Algorithm 39 of \cite{chambolle2010} to problem \eqref{eq:unconstrained_pb} we obtain Algorithm \ref{Tab:algo_simplified}. Its $\mathcal{O}(1/\epsilon)$ convergence rate in terms of the duality gap is immediate. Indeed,
%% \subsection{Special case: $C_k = \mathbb{R}^{n_k}_+$} As discussed in subsection \ref{subsec:example_games},
%% the Nash equilibrium problem for two-person zero-sum simultaneous games and two-person zero-sum sequential games with imcomplete
%% information and perfect recall admits the formulation \eqref{eq:primal_pb}, with $C_k = \mathbb{R}^{n_k}_+$ (coding for nonnegativity constraints).
%% In such situations, $\Pi_{C_k}(z) \equiv (z)_+$ as already mentioned in \ref{sec:notation}, and Algorithm \ref{Tab:algo} reduces to the simpler Algorithm \ref{Tab:algo_simplified}.
